Open-source tools in R for landscape ecology

### 2021-02-08 paper/paper.Rmd
add in LJG funding
Final polishing

\begin{tabularx}{450pt}{lX}

@@

(ref:fig1cap) Exemplary workflow of spatial data analyses for landscape ecology using the *R* programming language. For all major tasks, some example *R* packages are listed.
```{r fig-workflow, echo = FALSE, out.width="100%", out.height="30%", fig.cap = "(ref:fig1cap)"}
include_graphics("data/Workflow.png")
```

@@

(ref:capfigmap) Comparison of different options to create maps using a) base plot, b) *ggplot2* package, and c) *tmap* package. All maps show the total annual precipitation of Switzerland. Data were downloaded with the *raster* package (precipitation data) and *rnaturalearth* package (country borders) package. The code to create the maps can be found in the Appendix.
```{r fig-map, echo = FALSE, out.width="100%", out.height="50%", fig.cap = "(ref:capfigmap)"}
include_graphics("data/plot_all.pdf")
```

@@

\begin{tabularx}{450pt}{lrXr}

@@

\end{table}
```
# Survey of *R* usage by landscape ecology community

@@

To better understand how the landscape ecology community uses *R*, we conducted a short survey using mailing lists and social media to reach the community.
In total, the survey was answered by `r n_people` participants, of which the majority were either "PhD students" (`r current_position[[1, 2]]`%), followed by "Post-Docs" (`r current_position[[2, 2]]`%) and "Professors" (`r current_position[[3, 2]]`%).
Other, less frequent answers were "Data scientists", "None of the above", "Government employees" "Master's degree student" and "Bachelor's degree student" (in decreasing order).

@@

(ref:fig3cap) Results of the online survey about open-source software tools in *R* for landscape ecology. Results include a) which terms describe major research topics the best, b) the most important workflow task, c) the most used *R* packages and d) the overall usefulness or *R* for landscape ecology. The 'others' category includes all answers with less than five total mentions.

```{r fig-survey, echo = FALSE, fig.align="center", fig.cap = "(ref:fig3cap)", warning=FALSE, out.width="100%"}

@@

A comprehensive collection of *R* software packages exist to handle the most common tasks of landscape ecology. 
Because it is possible to import, modify, analyze, and visualize spatial data all in the same programming environment, *R* allows for transparent and reproducible workflows.
Additionally, this also allows users to easily interchange, modify, or adapt methods from other related and unrelated fields.

@@

@@

MHKH was supported by the German Research Association (DFG) Research Training Group 1644 'Scaling Problems in Statistics', grant number 152112243.

>>>>

\begin{tabularx}{1.15\textwidth}{lX}

@@

(ref:fig1cap) Exemplary workflow of spatial data analyses for landscape ecology using the *R* programming language. For all major tasks, some example *R* packages are listed.
```{r fig-workflow, echo = FALSE, out.width="\\linewidth", fig.cap = "(ref:fig1cap)"}
include_graphics("data/Figure_1.pdf")
```

@@

(ref:capfigmap) Comparison of different options to create maps using a) base plot, b) *ggplot2* package, and c) *tmap* package. All maps show the total annual precipitation of Switzerland. Data were downloaded with the *raster* package (precipitation data) and *rnaturalearth* package (country borders) package. The code to create the maps can be found in the Appendix.
```{r fig-map, echo = FALSE, out.width="\\linewidth", fig.cap = "(ref:capfigmap)"}
include_graphics("data/Figure_2.pdf")
```

\FloatBarrier

@@

\begin{tabularx}{1.35\linewidth}{lrXr}

@@

\end{table}
```

\FloatBarrier

# Survey of *R* usage by landscape ecology community

@@

To better understand how the landscape ecology community uses *R*, we conducted a short survey using mailing lists and social media to reach the community. 
All raw data and scripts to analyze the data can be found at [https://github.com/r-spatialecology/Hesselbarth_et_al_CLER](https://github.com/r-spatialecology/Hesselbarth_et_al_CLER).

In total, the survey was answered by `r n_people` participants, of which the majority were either "PhD students" (`r current_position[[1, 2]]`%), followed by "Post-Docs" (`r current_position[[2, 2]]`%) and "Professors" (`r current_position[[3, 2]]`%).
Other, less frequent answers were "Data scientists", "None of the above", "Government employees" "Master's degree student" and "Bachelor's degree student" (in decreasing order).

@@

(ref:fig3cap) Results of the online survey about open-source software tools in *R* for landscape ecology. Results include a) which terms describe major research topics the best, b) the most important workflow task, c) the most used *R* packages and d) the overall usefulness or *R* for landscape ecology. The 'others' category includes all answers with less than five total mentions.
```{r fig-survey, echo = FALSE, fig.align="center", fig.cap = "(ref:fig3cap)", warning=FALSE, out.width="\\textwidth"}

@@

A comprehensive collection of *R* software packages exists to handle the most common tasks of landscape ecology. 
Because it is possible to import, modify, analyze, and visualize spatial data all in the same programming environment, *R* allows for transparent and reproducible workflows.
Additionally, this also allows users to easily interchange, modify, or adapt methods from other related and unrelated fields.

@@

\FloatBarrier

@@

No funding was received by the authors for this research and publication.

####  Availability of data and material (data transparency)

All raw data and scripts to analyze the data can be found at [https://github.com/r-spatialecology/Hesselbarth_et_al_CLER](https://github.com/r-spatialecology/Hesselbarth_et_al_CLER).

### 2021-02-08 paper/paper.tex
Final polishing

\begin{figure}
\includegraphics[width=1\linewidth,height=0.3\textheight]{data/Workflow} \caption{Exemplary workflow of spatial data analyses for landscape ecology using the \emph{R} programming language. For all major tasks, some example \emph{R} packages are listed.}\label{fig:fig-workflow}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth,height=0.5\textheight]{data/plot_all} \caption{Comparison of different options to create maps using a) base plot, b) \emph{ggplot2} package, and c) \emph{tmap} package. All maps show the total annual precipitation of Switzerland. Data were downloaded with the \emph{raster} package (precipitation data) and \emph{rnaturalearth} package (country borders) package. The code to create the maps can be found in the Appendix.}\label{fig:fig-map}
\end{figure}

@@

To better understand how the landscape ecology community uses \emph{R}, we conducted a short survey using mailing lists and social media to reach the community.
In total, the survey was answered by 109 participants, of which the majority were either ``PhD students'' (33\%), followed by ``Post-Docs'' (26.6\%) and ``Professors'' (14.7\%).
Other, less frequent answers were ``Data scientists,'' ``None of the above,'' ``Government employees'' ``Master's degree student'' and ``Bachelor's degree student'' (in decreasing order).

@@

{\centering \includegraphics[width=1\linewidth]{paper_files/figure-latex/fig-survey-1}

@@

A comprehensive collection of \emph{R} software packages exist to handle the most common tasks of landscape ecology.
Because it is possible to import, modify, analyze, and visualize spatial data all in the same programming environment, \emph{R} allows for transparent and reproducible workflows.
Additionally, this also allows users to easily interchange, modify, or adapt methods from other related and unrelated fields.

@@

MHKH was supported by the German Research Association (DFG) Research Training Group 1644 `Scaling Problems in Statistics,' grant number 152112243.

>>>>

\begin{figure}
\includegraphics[width=\linewidth]{data/Figure_1} \caption{Exemplary workflow of spatial data analyses for landscape ecology using the \emph{R} programming language. For all major tasks, some example \emph{R} packages are listed.}\label{fig:fig-workflow}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{data/Figure_2} \caption{Comparison of different options to create maps using a) base plot, b) \emph{ggplot2} package, and c) \emph{tmap} package. All maps show the total annual precipitation of Switzerland. Data were downloaded with the \emph{raster} package (precipitation data) and \emph{rnaturalearth} package (country borders) package. The code to create the maps can be found in the Appendix.}\label{fig:fig-map}
\end{figure}

\FloatBarrier

@@

To better understand how the landscape ecology community uses \emph{R}, we conducted a short survey using mailing lists and social media to reach the community.
All raw data and scripts to analyze the data can be found at \url{https://github.com/r-spatialecology/Hesselbarth_et_al_CLER}.

In total, the survey was answered by 109 participants, of which the majority were either ``PhD students'' (33\%), followed by ``Post-Docs'' (26.6\%) and ``Professors'' (14.7\%).
Other, less frequent answers were ``Data scientists,'' ``None of the above,'' ``Government employees'' ``Master's degree student'' and ``Bachelor's degree student'' (in decreasing order).

@@

{\centering \includegraphics[width=\textwidth]{paper_files/figure-latex/fig-survey-1}

@@

A comprehensive collection of \emph{R} software packages exists to handle the most common tasks of landscape ecology.
Because it is possible to import, modify, analyze, and visualize spatial data all in the same programming environment, \emph{R} allows for transparent and reproducible workflows.
Additionally, this also allows users to easily interchange, modify, or adapt methods from other related and unrelated fields.

@@

No funding was received by the authors for this research and publication.

\hypertarget{availability-of-data-and-material-data-transparency}{%
\paragraph{Availability of data and material (data transparency)}\label{availability-of-data-and-material-data-transparency}}

All raw data and scripts to analyze the data can be found at \url{https://github.com/r-spatialecology/Hesselbarth_et_al_CLER}.
